Extracting Application and Menu Events from UI Tutorial Videos

### 2015-05-11 paper/main.tex
Paper: Added my draft of a section.

This will be Andrew's section.

Answer these questions:
\begin{enumerate}[noitemsep]
\item What is our dataset?
\item How did we construct/acquire it?
\item What's its size?
\item (optional) How will we improve it in the future?
\end{enumerate}

Here's a figure of our (edit: Andrew's) pipeline.  \textbf{Andrew: Add figure of pipeline.}

Here we (edit: Andrew) want to touch upon:
\begin{enumerate}[noitemsep]
\item How reliably can we classify UI events?
\item How long does it take for us to process one minute of video?  What are
the practical implications of this?
\item Some images that show recognition results for a few representative
screenshots of user interfaces.
\end{enumerate}

>>>>

Recent work~\cite{banovic_waken_2012} has shown how to extract templates for cursors and icons by
monitoring pixel differences across frames.  While there has been some initial efforts
towards recognizing tooltips and menus~\cite{banovic_waken_2012}, this task still lacks a
satisfying solution, given that reliable techniques to identify menu-based events could enable
automatic assessment of usability from UI video.

Detecting menus based on pixel difference between frames poses three challenges.  First, compressed 
video contains frame-to-frame noise that clouds the signal of a change in UI appearance, 
particularly if UI widgets tend to fade in or out gradually.  Second, these menus occlude
heterogeneous backgrounds (photos in Photoshop, colorful code in the IDE), making the difference
at each individual pixel highly-varied relative to its neighbors when a new object appears in the
foreground, even if it is of homogeneous color.  Third, depending on the operating system, 
the edges dividing menus from ribbons and borders in the main UI may be subtle compared to the
internal edges in a menu caused by text or internal horizontal lines that separate groups of options.
This makes it impossible to apply traditinoal segmentation techniques to extract menu regions from 
static images.

\begin{figure}
    \centering
    \begin{subfigure}{0.3\textwidth}
        \includegraphics[width=\textwidth]{fig/pipeline1}
        \caption{}
        \label{fig:pipeline1}
        \vspace*{2mm}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \includegraphics[width=\textwidth]{fig/pipeline2}
        \caption{}
        \label{fig:pipeline2}
        \vspace*{2mm}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \includegraphics[width=\textwidth]{fig/pipeline3}
        \caption{}
        \label{fig:pipeline3}
        \vspace*{2mm}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \includegraphics[width=\textwidth]{fig/pipeline4}
        \caption{}
        \label{fig:pipeline4}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \includegraphics[width=\textwidth]{fig/pipeline5}
        \caption{}
        \label{fig:pipeline5}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \includegraphics[width=\textwidth]{fig/pipeline6}
        \caption{}
        \label{fig:pipeline6}
    \end{subfigure}
    \caption{Our pipeline for extracting UI menu locations from a sequence of video frames.}
\end{figure}

We propose a method for extracting regions containing menus based on frame-to-frame pixel
differences.  We address the first two of the three detection challenges described above.

Our pipeline comprises three major steps.  First, we perform \emph{temporal smoothing}
of frame-to-frame pixel differences by averaging pixel differences over a window of size 10 
(Figure~\ref{fig:pipeline2}).  This reduces noise due to compression and enables us to detect
menus that fade in instead of appearing instantly.  10 frames is one-third of a second in a $29.97fps$ video, 
long enough to capture the entire fade-in of a menu in Windows 7 (3-5 frames)
and short enough to avoid capturing multiple menu actions in the same window.  Second, we \emph{coalesce
pixel differences} into a blob that spans the menu.  We perform heavy smoothing to remove
discontinuities in edge segments and bridge blobs from menu text (Figure~\ref{fig:pipeline3}).
We binarize the smoothed image at a heuristically-determined threshold (Figure~\ref{fig:pipeline4}).
Finally, we use existing methods for contour detection to trace the blob outline (Figure~\ref{fig:pipeline5}),
from which we take a rectangular bounding box as a region proposal (Figure~\ref{fig:pipeline6}).
We ignore all blobs that are smaller than 5000 pixels (around $70x70$ pixels square) to filter
out false positives from noisy regions of the screen.

To test our technique, we found 33 menu appearance events in 5 tutorial videos about Android development
in the Eclipse IDE.  This sample covered 3 different operating systems.
For each menu appearance, we selected the first frame where the menu was fully opaque in the video
(i.e., after fade-in) and manually determined its ground truth bounding box.

The quality of our region proposals is promising.  Our technique locates region proposal that
overlapping with the ground truth in 30/33 (91\%) of the test events.  We see an average 
intersection-over-union of 74\%.  Our technique produced only 2 false positive bounding rectangles 
for all menu appearances.  We note that the strength of our technique varies depending
on operating system.  For example, our system produced low-overlap region proposals
on a computer like Windows 2000, where the menu and application background color were likely
indistinguishable to our difference detection methods (Figure~\ref{fig:proposal5}, Figure~\ref{fig:proposal6}).

\begin{figure}
    \centering
    \begin{subfigure}{0.15\textwidth}
        \includegraphics[width=\textwidth]{fig/proposal1}
        \caption{}
        \label{fig:proposal1}
        \vspace*{2mm}
    \end{subfigure}
    \begin{subfigure}{0.15\textwidth}
        \includegraphics[width=\textwidth]{fig/proposal2}
        \caption{}
        \label{fig:proposal2}
        \vspace*{2mm}
    \end{subfigure}
    \begin{subfigure}{0.15\textwidth}
        \includegraphics[width=\textwidth]{fig/proposal3}
        \caption{}
        \label{fig:proposal3}
        \vspace*{2mm}
    \end{subfigure}
    \begin{subfigure}{0.15\textwidth}
        \includegraphics[width=\textwidth]{fig/proposal4}
        \caption{}
        \label{fig:proposal4}
        \vspace*{2mm}
    \end{subfigure}
    \begin{subfigure}{0.15\textwidth}
        \includegraphics[width=\textwidth]{fig/proposal5}
        \caption{}
        \label{fig:proposal5}
        \vspace*{2mm}
    \end{subfigure}
    \begin{subfigure}{0.15\textwidth}
        \includegraphics[width=\textwidth]{fig/proposal6}
        \caption{}
        \label{fig:proposal6}
        \vspace*{2mm}
    \end{subfigure}
\end{figure}

Our technique shows promise for extracting menu regions from UI videos.  We took preliminary efforts
to determine how to detect frame indexes where menus appear.  We hypothesize that frames with a 
high absolute pixel difference over their predecessors contained UI events.  To test his hypothesis, 
we extracted frames from one tutorial video for which the absolute pixel difference in the last 10
frames was in the 90th percentile of all differences.  Taking a sample of 50 of these frames, we confirmed that
\emph{nearly all} frames in this percentile showed a UI event in progress.  Of these, only 6 (12\%) 
were menu appearances or disappearances.  We conclude that while pixel difference-based inspection of frames may lead to
high precision detection of UI events in general, more specialized techniques are needed to
delineate menu-based UI events from application switches, window repainting, and window
appearances and disappearances in the future.
